### 2022-04-07 README.Rmd
tiny updates to README

The simplest way to explore the text, code and data is to click on
[binder](https://mybinder.org/v2/gh/BiomarkABS/DeadwaterPaper/main?urlpath=rstudio)
to open an instance of RStudio in your browser, which will have the
compendium files ready to work with. Binder uses rocker-project.org
Docker images to ensure a consistent and reproducible computational
environment. These Docker images can also be used locally.

>>>>

The simplest way to explore the text, code and data is to click on
[binder](https://mybinder.org/v2/gh/mackerman44/DeadwaterPaper/main?urlpath=rstudio)
to open an instance of RStudio in your browser, which will have the
compendium files ready to work with. Binder uses rocker-project.org
Docker images to ensure a consistent and reproducible computational
environment. These Docker images can also be used locally.
